\SW: II. New lens candidates from the CFHTLS discovered through citizen science

### 2015-04-12 doc/sw-cfhtls.tex
read through all sections

We begin by considering all elliptical galaxies at $z<1$ in our parent
\cfhtls catalog \citep[(XXX confirm with Raphael)]{Gavazzi2014} as
potential lens candidates for the simulated sample. To avoid using a
known lens galaxy for our simulation purpose, we exclude all those
galaxies whose positions match with the lensing galaxies from the SARCS
samples within 2~arcsec (XXX check).

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.3]{sw-cfhtls-figs/lensprop.pdf}
\caption{ \label{fig:lensprop}
Distributions of properties of the lensing galaxies of the simulated
sample compared to the known lens sample SARCS. %(XXXX confirm what's being plotted? which band - i?)
}
\end{center}
\end{figure*}

@@

In this section, we describe the \sw-\cfhtls lens sample (henceforth,
called the \sw lens sample). We find a total of XXX (and XXX new)
candidates with averaged grade $0<$G$<1.3$ (low probability sample)
which means - in the worst case, at least one of the inspector thought
the candidate is possibly a lens and in the best case, all three
inspectors thought the candidate is possibly a lens (that is,
a grade of 1)\footnote{If grades from the inspectors were found to be discrepant
by 2 or more, these were discussed and re-graded to resolve the
discrepancy.}. Further information on the low probability sample such as
their positions and images is available at
http://spacewarps.org/\#/projects/CFHTLS/. Note that if all of the inspectors gave
a grade of 0 to a candidate, then it is discarded from the sample.

@@

Indeed, we have found several new lens candidates that were not known
before. In \Fref{fig:isd}, we show the image separation distribution for
the known \rf and \af sample (green), for the \sw identified (known and
new) lens sample (blue) only and combined \cfhtls sample of \rf, \af and
the new \sw lens sample (magenta). It is interesting to note that both
these samples have very similar profiles and thus, the profile of the
combined sample has not changed signficantly. This implies that previous
constraints on the image separation distribution are robust and the \af
selected sample does not suffer from significant incompleteness for
medium to large Einstein radii. This is the regime that probes density
profiles of galaxy groups to clusters.
%%{\bf AM: understand what Phil wanted to say about AF's (in)completeness}

@@

The properties considered here do not show any clear differences between
the types of lenses being found by each method. Other properties such as
the flux of the lensing galaxies and the surface brightness of the
lensed images may be useful in showing some qualitative differences but
this is beyond the scope of our current analysis. A more detailed and
accurate analysis is deferred to the future.
%{\bf check out of the 55 promising \af how many are missed by \sw ?}

@@

%{ Let us compare the two samples to see if there are any obvious differences. only 2 out of this sample of 18 were detected at \StageOne (reached high P even with fewer classifications) and missed at \StageTwo (P value was low even after recieving very many classifications). The rest of the 16 lenses were rejected right at \StageOne XXX}
%One of those 6 lenses was detected at \StageOne but failed to get high enough P value at \StageTwo even after receiving a total of 50 classifications (set as the upper limit). The rest of the 5 lenses are already rejected at \StageOne. Upon visual inspection of these 5 systems, they appear to be difficult to identify as lenses because either the lensed images are faint, have low curvature, are close to the edge and/or are not visible due to proximity to an extremely bright galaxy

>>>>

We begin by considering all elliptical galaxies at $z<1$ in our parent
\cfhtls catalog \citep[(XXX confirm with Raphael)]{Gavazzi2014} as
potential lens candidates for the simulated sample. To avoid using a
known lens galaxy for our simulation purpose, we exclude all those
galaxies whose positions match with the lensing galaxies from the SARCS
samples within 2~arcsec.

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.3]{sw-cfhtls-figs/lensprop.pdf}
\caption{ \label{fig:lensprop}
Distributions of properties of the lensing galaxies of the simulated
sample compared to the known lens sample SARCS. 
}
\end{center}
\end{figure*}

@@

In this section, we describe the \sw-\cfhtls lens sample (henceforth,
called the \sw lens sample). We find a total of  (and XXX new)
candidates with averaged grade $0<$G$<1.3$ (low probability sample)
which means - in the worst case, at least one of the inspector thought
the candidate is possibly a lens and in the best case, all three
inspectors thought the candidate is possibly a lens (that is,
a grade of 1)\footnote{If grades from the inspectors were found to be discrepant
by 2 or more, these were discussed and re-graded to resolve the
discrepancy.}. Further information on the low probability sample such as
their positions and images is available at
http://spacewarps.org/\#/projects/CFHTLS/. Note that if all of the inspectors gave
a grade of 0 to a candidate, then it is discarded from the sample.

@@

Indeed, we have found several new lens candidates that were not known
before. In \Fref{fig:isd}, we show the image separation distribution for
the known \rf and \af sample (green), for the \sw identified (known and
new) lens sample (blue) only and combined \cfhtls sample of \rf, \af and
the new \sw lens sample (magenta). It is interesting to note that both
these samples have very similar profiles and thus, the profile of the
combined sample has not changed signficantly. This implies that previous
constraints on the image separation distribution are robust and the \af
selected sample does not suffer from significant incompleteness for
medium to large Einstein radii. This is the regime that probes density
profiles of galaxy groups to clusters.

@@

The properties considered here do not show any clear differences between
the types of lenses being found by each method. Other properties such as
the flux of the lensing galaxies and the surface brightness of the
lensed images may be useful in showing some qualitative differences but
this is beyond the scope of our current analysis. A more detailed and
accurate analysis is deferred to the future.

@@

%{ Let us compare the two samples to see if there are any obvious differences. only 2 out of this sample of 18 were detected at \StageOne (reached high P even with fewer classifications) and missed at \StageTwo (P value was low even after recieving very many classifications). The rest of the 16 lenses were rejected right at \StageOne }
%One of those 6 lenses was detected at \StageOne but failed to get high enough P value at \StageTwo even after receiving a total of 50 classifications (set as the upper limit). The rest of the 5 lenses are already rejected at \StageOne. Upon visual inspection of these 5 systems, they appear to be difficult to identify as lenses because either the lensed images are faint, have low curvature, are close to the edge and/or are not visible due to proximity to an extremely bright galaxy
